The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-02-20 paper.tex
elaborate a little bit on the source removal process

The 288 antennas are arranged in a maximally non-redundant configuration optimized for minimum
sidelobes in snapshot imaging. 251 of these antennas are contained within a 200 m diameter core that
is independently optimized for imaging sidelobe levels. 32 antennas are placed outside of the core
in order to extend the maximum baseline length out to $\sim$1.5 km. The final 5 antennas are
equipped with noise-switched front ends for calibrated total power measurements of the global sky
brightness. These antennas are used as part of the LEDA experiment to measure the global signal of
21 cm absorption from the cosmic dawn. \todo{cite a leda paper} Calibrated total power measurements
from these antennas will be used to constrain sky modes with $l \lesssim 2$ including the monopole.

@@

At low frequencies, propagation effects through the ionosphere must be accounted for in order to
achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.

In the dataset used in this paper, scintillation and diffraction events on the timescale of a single
integration (13 seconds) are observed. Therefore the direction dependent calibration changes on
these timescales and the peeling routine must solve for one set of complex gains per source per
integration. Mild smoothing of the gain solutions along the frequency axis is possible without
degrading the dynamic range.

Given the angular resolution of the OVRO LWA and the angular extent of Cas A and Cyg A, these two
sources are marginally resolved and a simple point source model will not achieve the necessary
dynamic range. \todo{describe my source fitting routine}

\subsection{RFI Suppression}

The Owens Valley is an important source of water and power for the city of Los Angeles.
Unfortunately this means that high voltage power lines run along the valley to the west of the OVRO
LWA. Some of these power line poles have faulty insulators that arc and produce pulsed, broadband
RFI. Because these poles exist in the near-field of the array, we have been able to localize some of
them by using the curvature of the incoming wavefront. Efforts are currently underway to work with
the utility pole owners to have the arcing fixed.

@@

\subsection{Horizon RFI}

@@

\subsection{Scintillation}

@@

@@

\subsection{Peeling Failure}

>>>>

The 288 antennas are arranged in a maximally non-redundant configuration optimized for minimum
sidelobes in snapshot imaging. 251 of these antennas are contained within a 200 m diameter core that
is independently optimized for imaging sidelobe levels. 32 antennas are placed outside of the core
in order to extend the maximum baseline length out to $\sim$1.5 km. The final 5 antennas are
equipped with noise-switched front ends for calibrated total power measurements of the global sky
brightness. These antennas are used as part of the LEDA experiment to measure the global signal of
21 cm absorption from the cosmic dawn. \todo{cite a leda paper} Calibrated total power measurements
from these antennas will be used to constrain sky modes with $l \lesssim 2$ including the monopole.
\todo{What values of $l$ actually contribute to the total power measurements?}

@@

\subsubsection{Cassiopeia A and Cygnus A}

Without removing bright sources from the data, sidelobes from bright sources will dominate the
variance in the image.  At 74 MHz Cyg A is a 15,000 Jy source \citep{2016arXiv160905940P}. A
conservative estimate for the confusion limit at 74 MHz with a 10 arcminute beam is 500 mJy
\citep{2012RaSc...47.0K04L}. Therefore we require that Cyg A's sidelobes be at most of $-$45 dB down
from its peak flux to prevent Cyg A's sidelobes from dominating the variance in the image.
\todo{Measure Cyg A's sidelobe levels if it is not subtracted}

At low frequencies, propagation effects through the ionosphere must be accounted for in order to
achieve high dynamic range images. This necessitates the use of direction-dependent calibration and
peeling \citep{2008ISTSP...2..707M, 2015MNRAS.449.2668S}.  In the dataset used in this paper,
scintillation and diffraction events on the timescale of a single integration (13 seconds) are
observed. Therefore the direction dependent calibration changes on these timescales and the we must
solve for one set of complex gains per source per integration.

The largest angular scale of Cas A is $\sim$8 arcminutes, while the largest angular scale of Cyg A
is $\sim$2 arcminutes. With a 10 arcminute resolution, the OVRO LWA marginally resolves both
sources. A resolved source model is needed for both sources. We fit a self-consistent resolved
source model to eachs ource. This is performed by minimizing the minimizing the variance within an
aperture located on each source after peeling. By phasing up a large number of integrations before
imaging (at least over 1 hour) it is possible to smear out the contribution of the rest of the sky.
We then use NLopt's Sbplx routine \citep{nlopt, sbplx} to vary the parameters in a source model
until the variance within the aperture is minimized.

\todo{Show a before and after with the updated source models}

\todo{Give a plot with the updated source models}

\subsubsection{The Sun}

The Sun can be trivially removed from any map of the sky by constructing the map using only data
taken at night. A map of the entire sky can be obtained by using observations spaced 6 months apart.
However the OVRO LWA 100 hour dataset consists of 100 consecutive hours of data, and hence roughly
half of the data is from the day.

The Sun is a time variable source in radio.

\todo{does the previous routine work on the Sun too? worth a shot}

\subsubsection{Sparking Power Lines}

The Owens Valley is an important source of water and power for the city of Los Angeles.
Unfortunately this means that high voltage power lines run along the valley to the west of the OVRO
LWA. Some of these power line poles have faulty insulators that arc and produce pulsed, broadband
RFI. Because these poles exist in the near-field of the array, we have been able to localize some of
them by using the curvature of the incoming wavefront. Efforts are currently underway to work with
the utility pole owners to have these insulators replaced.

@@

\subsection{Stationary Correlated Noise}

@@

\subsection{Ionospheric Scintillation}

@@

\subsection{Ionospheric Refraction}

@@
